Papers I Love

### 2017-04-19 texts/dev/PapersILove.tex
reactive system paper
Design Patterns for Generic Programming in C++

\subsubsection{Process Algebra}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
	\item {Some of My Favourite Results in Classic Process Algebra (Version of September 9, 2003)\\
\url{https://www.researchgate.net/publication/228785318_Some_of_My_Favourite_Results_in_Classic_Process_Algebra_Version_of_September_9_2003}}
\end{enumerate}

@@

\subsubsection{Resiliency}
\begin{enumerate}
	\item {Adaptive Overload Control for Busy Internet Servers\\
\href{http://academic.research.microsoft.com/Publication/634136/adaptive-overload-control-for-busy-internet-servers}{http://academic.research.microsoft.com/Publication/634136/adaptive-overload-control-for-busy-internet-servers}\\
\url{http://www.eecs.harvard.edu/~mdw/papers/control-usits03.pdf}}
\end{enumerate}

\subsection{Programming Paradigms}
\subsubsection{Process Theory}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
\end{enumerate}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}
\subsubsection{Double Dispatch}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

>>>>

\subsubsection{Process Algebra}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
	\item {Some of My Favourite Results in Classic Process Algebra (Version of September 9, 2003)\\
\url{https://www.researchgate.net/publication/228785318_Some_of_My_Favourite_Results_in_Classic_Process_Algebra_Version_of_September_9_2003}}
	\item {Reactive Systems: Modelling, Speciﬁcation and Veriﬁcation\\
\url{https://www.semanticscholar.org/paper/Reactive-Systems-Modelling-Specification-and-Aceto-Larsen/454e1c72efc65270649e10efb11f4390606b7ea7}}
\end{enumerate}

@@

\subsubsection{Resiliency}

\begin{enumerate}
	\item {Adaptive Overload Control for Busy Internet Servers\\
\href{http://academic.research.microsoft.com/Publication/634136/adaptive-overload-control-for-busy-internet-servers}{http://academic.research.microsoft.com/Publication/634136/adaptive-overload-control-for-busy-internet-servers}\\
\url{http://www.eecs.harvard.edu/~mdw/papers/control-usits03.pdf}}
\end{enumerate}

\subsection{Programming Paradigms}
\subsubsection{Process Theory}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
\end{enumerate}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}

\subsubsection{Generic Programming}
	\begin{enumerate}
	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.htmls}}
	\end{enumerate}
\subsubsection{Dynamic Dispatch}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}
